---
output: html_document
---

\setlength{\parindent}{0in}
\setlength{\leftskip}{0in}
\normalsize

```{r, results='asis'}
nice_header("Other Research Experience", "Autres expériences de recherche", language)
```

`r if_english("## PhD Intern, [Max Planck Social Neuroscience Lab - Tania Singer](https://www.social.mpg.de/2766/en)", "## Stagiaire doctoral, [Max Planck Social Neuroscience Lab - Tania Singer](https://www.social.mpg.de/2766/en)", language)`

```{r experience_new, include = TRUE, eval=TRUE}

exp_dictionary <- tribble(
  ~English, ~French,
  "Edu:Social School: Strengthening Resilience and Social Skills Among Teachers",
    "Edu:Social École : Renforcer la résilience et les compétences sociales des enseignants",
  "Berlin, Germany", "Berlin, Allemagne",
  "Contributed to conceiving research design, formulating hypotheses, designing new tasks, \\\\& reviewing litterature",
    "Conception du plan de recherche, formulation d'hypothèses, conception de nouvelles tâches et révision de la littérature.",
  "Contributed to admin documents: clinical trial, preregistration, ethics, senate application, etc.",
    "Contribution aux documents administratifs : essai clinique, pré-inscription, éthique, demande au Sénat, etc.",
  "Topic 1: Social emotions (empathy and compassion)",
    "Thème 1 : Les émotions sociales (empathie et compassion)",
  "Topic 2: Social interactions (egocentric social network analysis)",
    "Thème 2 : Interactions sociales (analyse égocentrique des réseaux sociaux)",
  "Various research projects", "Divers projets de recherche",
  "Sensory Deprivation, Consciousness, and Dissociation",
    "Privation sensorielle, conscience et dissociation",
  "Posture and Human Resting-State (EEG, MEG)",
    "Posture et état de repos humain (EEG, MEG)",
  "Chronic Hives and the Effect of Cognitive Treatment in Kids and Adults",
    "Urticaire chronique et effet du traitement cognitif chez les enfants et les adultes",
  "Attention Training in Health and Disease",
    "Formation à l'attention en matière de santé et de maladie"
)
data <- rbind(
  
  tibble(
    what = "Edu:Social School: Strengthening Resilience and Social Skills Among Teachers",
    URL = "https://www.edusocial-project.de/en/",
    when = "2023/10-2024/05",
    with = "Max Planck Social Neuroscience Lab",
    where = "Berlin, Germany",
    details = c("Contributed to conceiving research design, formulating hypotheses, designing new tasks, \\& reviewing litterature",
                "Contributed to admin documents: clinical trial, preregistration, ethics, senate application, etc.",
                "Topic 1: Social emotions (empathy and compassion)",
                "Topic 2: Social interactions (egocentric social network analysis)")))

data <- data %>% 
  mutate(what = link(what, URL, color = "333333"))

nice_entries(data, language, exp_dictionary)

```

`r if_english("## Research Assistant, [McGill Cognitive Neuroscience Lab - Amir Raz](https://raz-lab.org/)", "## Assistant de recherche, [McGill Cognitive Neuroscience Lab - Amir Raz](https://raz-lab.org/)", language)`

```{r experience, include = TRUE}
data <- rbind(
  
  tibble(
    what = "Various research projects",
    URL = "",
    when = "2013/09–2016/09",
    with = "McGill Cognitive Neuroscience Lab",
    where = "Montréal, Québec",
    details = c(
      link(
        "Sensory Deprivation, Consciousness, and Dissociation",
        "https://digitalcommons.chapman.edu/cusrd_abstracts/325/",
        "333333"),
      link(
        "Posture and Human Resting-State (EEG, MEG)",
        "https://escholarship.mcgill.ca/concern/theses/bz60cz84m",
        "333333"),
      link(
        "Chronic Hives and the Effect of Cognitive Treatment in Kids and Adults",
        "https://escholarship.mcgill.ca/concern/theses/2f75rb82q",
        "333333"),
      link(
        "Attention Training in Health and Disease",
        "https://escholarship.mcgill.ca/concern/theses/12579w270",
        "333333")
      ))#,
  
  # tibble(
  #   what = "Sensory Deprivation, Consciousness, and Dissociation",
  #   URL = "https://digitalcommons.chapman.edu/cusrd_abstracts/325/",
  #   when = "2014/09-2016/09",
  #   with = "McGill Cognitive Neuroscience Lab",
  #   where = "Montréal, Québec",
  #   details = c("Conceived research designs \\& formulated hypotheses",
  #               "Performed various administrative tasks related to the sensory deprivation unit (shopping, maintenance, risks, authorizations, etc.)")),

  # tibble(
  #   what = "Administrative Assistantship",
  #   when = "2013/09-2016/09",
  #   with = "McGill Cognitive Neuroscience Lab",
  #   where = "Montréal, Québec",
  #   details = c("Worked on the WordPress website (razlab.org) \\& managed servers",
  #               "Edited videos and photos",
  #               "Performed various investigations on different topics for PI")),
  # 
  # tibble(
  #   what = "Posture and Human Resting-State (EEG, MEG)",
  #   URL = "https://escholarship.mcgill.ca/concern/theses/bz60cz84m",
  #   when = "2015/05-07",
  #   with = "McGill Cognitive Neuroscience Lab",
  #   where = "Montréal, Québec",
  #   details = "Performed various tasks (including statistical analyses) on Brainstorm, Matlab, and Photoshop"),
  # 
  # tibble(
  #   what = "Chronic Hives and the Effect of Cognitive Treatment in Kids and Adults",
  #   URL = "https://escholarship.mcgill.ca/concern/theses/2f75rb82q",
  #   when = "2014/01-09",
  #   with = "McGill Cognitive Neuroscience Lab",
  #   where = "Montréal, Québec",
  #   details = "Recruited and managed participants’ appointments"),
  # 
  # tibble(
  #   what = "Attention Training in Health and Disease",
  #   URL = "https://escholarship.mcgill.ca/concern/theses/12579w270",
  #   when = "2014/05-08",
  #   with = "McGill Cognitive Neuroscience Lab",
  #   where = "Montréal, Québec",
  #   details = "Trained children’s attention with video games (data collection)")
  # 
  )

data <- data %>% 
  mutate(what = link(what, URL, color = "333333"))

nice_entries(data, language, exp_dictionary)

```
