---
output: html_document
---

\setlength{\parindent}{0in}
\setlength{\leftskip}{0in}
\normalsize

```{r, results='asis'}
nice_header("Varia", "Varia", language)
```

<!-- ## Professional Affiliations -->

\scriptsize

```{r Affiliations, eval=FALSE}
data <- rbind(
  
  tibble(
    when = "2021-01 – Present",
    with = "Institut des sciences cognitives (UQAM)"),
  
  tibble(
    when = "2016-09 – Present",
    with = "International Positive Psychology Association"),
  
  tibble(
    when = "2015-09 – Present",
    with = "Canadian Positive Psychology Association")
)

detailed_entries(data, with, when, .protect = FALSE)
```

<!-- ## Research Interests -->

<!-- Positive & moral psychology, contemplative practices, Theory of Mind, empathy, self-regulatory strength, Self-Determination Theory, bodily self-consciousness -->

`r if_english("## Technical Skills", "## Compétences techniques", language)`

R, Rstudio, Rmarkdown, Shiny, GitHub, Inquisit, Wowchemy, Netlify, SPSS, Qualtrics, Survey Monkey, LimeSurvey, Inkscape

`r if_english("## Languages", "## Langages", language)`

`r if_english("French (native), English (fluent)", "Français (langue natale), Anglais (fluent)", language)`

<!-- ## Activities and Interests -->

<!-- Martial arts, breakdancing, skateboarding, gymnastics, bouldering -->
