---
output: html_document
---

\scriptsize
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}

# Publications in Peer-Reviewed Journals

```{r, results = "asis", echo = FALSE, message = FALSE, eval = FALSE}
format.authors <- function(scholar.profile, author.name) {
  library(dplyr)

  swap_initials <- function(author.name) {
    sub("(.*) (.*)", "\\2, \\1.", trimws(author.name))
  }

  pubs <- scholar::get_publications(scholar.profile)
  pubs %>% 
    strsplit(x = .$author, split = ",") -> pubs2
  lapply(pubs2, function(x) {
    x <- swap_initials(x)
    x[length(x)] <- paste0("& ", x[length(x)])
    x <- paste0(x, collapse = ", ")
    ifelse(startsWith(x, "& "), sub("& ", "", x), x)
    }
    ) -> pubs$author
  
  author.name2 <- swap_initials(author.name)
  
  pubs %>% 
    arrange(desc(year)) %>%
    mutate(journal = paste0("*", journal, "*"),
           Publications = paste0(author, " (", year, "). ", 
                                 title, ". ", journal, ". ", 
                                 number),
           Publications = gsub(author.name2, paste0("**", author.name2, "**"), Publications)) %>% 
    select(Publications)
}

pubs <- format.authors("NrfwEncAAAAJ", "R Thériault")

cat(unlist(pubs), sep = "\\\n \\\n")

```

```{r, results = "asis"}
# print_latex(as_hux(pubs2))
```

12\. **Thériault, R.**, Dion-Cliche, F., & Dandeneau, S. (2023). Unmet expectations: Social inclusion and the interaction between social anxiety and ambiguous or positive feedback. *Frontiers in Psychology* (2022 IF = 3.8; 5-year IF = 4.3), 1-10. https://doi.org/10.3389/fpsyg.2023.1271773

11\. **Thériault, R.** & Dandeneau, S. (2023). Implicitly activating mindfulness: Does trait self-control moderate its effect on aggressive behaviour? *Mindfulness* (2022 IF = 3.6; 5-year IF = 4.7). https://doi.org/10.1007/s12671-023-02246-w (Preprint: https://doi.org/10.21203/rs.3.rs-3161372/v2)

10\. **Thériault**, R. (2023). lavaanExtra: Convenience functions for lavaan. *Journal of Open Source Software* (2022 IF = NA), *8*(90), 5701. https://doi.org/10.21105/joss.05701

9\. **Thériault**, R. (2023). rempsyc: Convenience functions for psychology. *Journal of Open Source Software* (2022 IF = NA), *8*(87), 5466. https://doi.org/10.21105/joss.05466

8\. Ben-Shachar, M. S., Patil, I., **Thériault, R.**, Wiernik, B. M., & Lüdecke, D. (2023). Phi, Fei, Fo, Fum: Effect Sizes for Categorical Data that Use the Chi-Squared Statistic. *Mathematics* (2022 IF = 2.4; 5-year IF = 2.3), *11*(9), 1982. https://doi.org/10.3390/math11091982

7\. Miglianico, M.\*, **Thériault, R.\*,** Lavoie, B.\*, Labelle, P., Joussemet, M., Veilleux, M., Lambert, J., & Bertrand-Dubois, D. (2022). Pratiques cliniques inspirées par la recherche en psychologie positive / Clinical practices inspired by research in positive psychology. *Psychologie Française* (2022 IF = 0.3; 5-year IF = 0.5). \*These authors contributed equally. https://doi.org/10.1016/j.psfr.2022.06.004

6\. **Thériault, R.**, Landry, M., & Raz, A. (2022). The Rubber Hand Illusion: Top-down attention modulates embodiment. *Quarterly Journal of Experimental Psychology* (2022 IF = 1.7; 5-year IF = 2.1), *75*(11), 2129-2148. https://doi.org/10.1177/17470218221078858

5\. **Thériault, R.**, Olson, J. A., Krol, S. A., & Raz, A. (2021). Body swapping with a black person boosts empathy: Using virtual reality to embody another. *Quarterly Journal of Experimental Psychology* (2022 IF = 1.7; 5-year IF = 2.1), 74(12), 2057-2074. https://doi.org/10.1177/17470218211024826

4\. Krol, S. A., **Thériault, R.**, Olson, J. A., Raz, A., & Bartz, J. (2020). Self-concept clarity and the bodily self: Malleability across modalities. *Personality and Social Psychology Bulletin* (2022 IF = 4.0; 5-year IF = 4.9), *46*(5). https://doi.org/10.1177/0146167219879126

3\. **Thériault, R.** (2019). Book review: Awareness is freedom: The adventure of psychology and spirituality. *Frontiers in Psychology* (2022 IF = 3.8; 5-year IF = 4.3), *10*(2814)*.* https://doi.org/10.3389/fpsyg.2019.02814

2\. **Thériault, R.**, & Raz, A. (2018). Patterns of bronchial challenge testing in Canada. *Canadian Journal of Respiratory Therapy* (2022 IF = NA), *54*(2), 41-47. https://doi.org/10.29390/cjrt-2018-006

1\. Lifshitz, M., Sheiner, E. O., Olson, J., **Thériault, R.**, & Raz, A. (2017). On suggestibility and placebo: A follow-up study. *American Journal of Clinical Hypnosis* (2022 IF = 1.3; 5-year IF = 1.2), *59*(4), 1-8. https://doi.org/10.1080/00029157.2016.1225252

```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="80%", fig.align="center", eval = !short}

source("../files/make_data_impact.R")
plot_impact(data_scholar)
table_impact(data_scholar, author.name = author.name)

```
