---
output: html_document
---

\scriptsize
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
<!-- \setlength{\parskip}{8pt} -->

# Publications

```{r, results = "asis", echo = FALSE, message = FALSE, eval = FALSE}
format.authors <- function(scholar.profile, author.name) {
  library(dplyr)

  swap_initials <- function(author.name) {
    sub("(.*) (.*)", "\\2, \\1.", trimws(author.name))
  }

  pubs <- scholar::get_publications(scholar.profile)
  pubs %>% 
    strsplit(x = .$author, split = ",") -> pubs2
  lapply(pubs2, function(x) {
    x <- swap_initials(x)
    x[length(x)] <- paste0("& ", x[length(x)])
    x <- paste0(x, collapse = ", ")
    ifelse(startsWith(x, "& "), sub("& ", "", x), x)
    }
    ) -> pubs$author
  
  author.name2 <- swap_initials(author.name)
  
  pubs %>% 
    arrange(desc(year)) %>%
    mutate(journal = paste0("*", journal, "*"),
           Publications = paste0(author, " (", year, "). ", 
                                 title, ". ", journal, ". ", 
                                 number),
           Publications = gsub(author.name2, paste0("**", author.name2, "**"), Publications)) %>% 
    select(Publications)
}

pubs <- format.authors("NrfwEncAAAAJ", "R Thériault")

cat(unlist(pubs), sep = "\\\n \\\n")

```

```{r, results = "asis"}
# print_latex(as_hux(pubs2))
```

16\. Ghai, S., **Thériault, R.**, Forscher, P., Shoda, Y., Syed, M., Puthillam, A., Peng, H. C., Basnight-Brown, D., Majid, A., Azevedo, F., Singh, L. (2025, In press). A manifesto for a globally diverse, equitable, and inclusive open science. *Communications Psychology*. 1-38.

15\. Cimon-Paquet, C., St-Cyr, J., **Thériault, R**., & Vallerand, R. J. (2025). Moving positive psychology forward: Building on the psychology of passion. *International Journal of Applied Positive Psychology*, *10*(14), 1-19. https://doi.org/10.1007/s41042-024-00198-7

14\. **Thériault**, R. (2025). L’importance de la science ouverte en recherche en psychologie [The importance of open science in psychological research]. Accepted in *Fragments : Revue de psychologie*, 1-15. Preprint: https://doi.org/10.31234/osf.io/758dx

13\. **Thériault**, R., Ben-Shachar, M. S., Patil, I., Lüdecke, D., Wiernik, B. M., & Makowski, D. (2024). Check your outliers! An introduction to identifying statistical outliers in R with *easystats*. *Behavior Research Methods*, *56*(4), 4162-4172. https://doi.org/10.3758/s13428-024-02356-w (Preprint: https://doi.org/10.31234/osf.io/bu6nt)

12\. Miglianico, M.\*, **Thériault, R.\*,** Lavoie, B.\*, Labelle, P., Joussemet, M., Veilleux, M., Lambert, J., & Bertrand-Dubois, D. (2024). Pratiques cliniques inspirées par la recherche en psychologie positive / Clinical practices inspired by research in positive psychology. *Psychologie Française*, *69*(1), 85-94. \*Shared first-authorship (these authors contributed equally). https://doi.org/10.1016/j.psfr.2022.06.004

11\. **Thériault, R.**, Dion-Cliche, F., & Dandeneau, S. (2023). Unmet expectations: Social inclusion and the interaction between social anxiety and ambiguous or positive feedback. *Frontiers in Psychology*, 14, 1-10. https://doi.org/10.3389/fpsyg.2023.1271773

10\. **Thériault, R.** & Dandeneau, S. (2023). Implicitly activating mindfulness: Does trait self-control moderate its effect on aggressive behaviour? *Mindfulness*, 14(12), 2946–2962. https://doi.org/10.1007/s12671-023-02246-w (Preprint: https://doi.org/10.21203/rs.3.rs-3161372/v2)

9\. **Thériault**, R. (2023). lavaanExtra: Convenience functions for lavaan. *Journal of Open Source Software*, *8*(90), 5701. https://doi.org/10.21105/joss.05701

8\. **Thériault**, R. (2023). rempsyc: Convenience functions for psychology. *Journal of Open Source Software*, *8*(87), 5466. https://doi.org/10.21105/joss.05466

7\. Ben-Shachar, M. S., Patil, I., **Thériault, R.**, Wiernik, B. M., & Lüdecke, D. (2023). Phi, Fei, Fo, Fum: Effect sizes for categorical data that use the chi-squared statistic. *Mathematics*, *11*(9), 1982. https://doi.org/10.3390/math11091982

6\. **Thériault, R.**, Landry, M., & Raz, A. (2022). The Rubber Hand Illusion: Top-down attention modulates embodiment. *Quarterly Journal of Experimental Psychology*, *75*(11), 2129-2148. https://doi.org/10.1177/17470218221078858

5\. **Thériault, R.**, Olson, J. A., Krol, S. A., & Raz, A. (2021). Body swapping with a black person boosts empathy: Using virtual reality to embody another. *Quarterly Journal of Experimental Psychology*, 74(12), 2057-2074. https://doi.org/10.1177/17470218211024826

4\. Krol, S. A., **Thériault, R.**, Olson, J. A., Raz, A., & Bartz, J. (2020). Self-concept clarity and the bodily self: Malleability across modalities. *Personality and Social Psychology Bulletin*, *46*(5). https://doi.org/10.1177/0146167219879126

3\. **Thériault, R.** (2019). Book review: Awareness is freedom: The adventure of psychology and spirituality. *Frontiers in Psychology*, *10*(2814)*.* https://doi.org/10.3389/fpsyg.2019.02814

2\. **Thériault, R.**, & Raz, A. (2018). Patterns of bronchial challenge testing in Canada. *Canadian Journal of Respiratory Therapy*, *54*(2), 41-47. https://doi.org/10.29390/cjrt-2018-006

1\. Lifshitz, M., Sheiner, E. O., Olson, J., **Thériault, R.**, & Raz, A. (2017). On suggestibility and placebo: A follow-up study. *American Journal of Clinical Hypnosis*, *59*(4), 1-8. https://doi.org/10.1080/00029157.2016.1225252

```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="80%", fig.align="center", eval = !short}

source("../files/make_data_impact.R")
plot_impact(data_scholar)
table_impact(data_scholar, author.name = author.name, scholar.profile = scholar.profile)

```

<!-- # Non-Peer-Reviewed Publications -->

<!-- **Thériault, R.** (2023). Bonnes pratiques et science ouverte : Un document d'accompagnement au PRD. <https://remi-theriault.com/files/science_ouverte2023.pdf> -->

<!-- **Thériault, R.**, Masson, R., & Dandeneau, S. (in preparation). Is the Mind More Powerful Than the Heart? A Randomized Controlled Trial of Two Loving-Kindness Interventions. -->

<!-- **Thériault, R.**, Dandeneau, S., & Baldwin, M. (in preparation). All in a smiling face: The attentional benefits of dynamic attention training for low self-esteem individuals. -->

<!-- **Thériault, R.**, Landry, M., Mattuck, S., and Raz, A. (in preparation). The Rubber Hand Illusion: Does cognitive load affect EEG & electrodermal activity? -->

<!-- **Thériault, R.**, Corber, L., MacLean, C. W., Napoleon, J.-S., Olson, J., Turkakin, E., & Raz, A. (in preparation). Suggestion affects subjective breathlessness but not objective pulmonary function. -->

<!-- **Thériault, R.** (2018). *Comparing the effects of mental and embodied perspective-taking* (Master's thesis). McGill University, Montréal, Québec, Canada. -->

<!-- **Thériault, R.** (2016). *Exploring cognitive dimensions of body ownership* (Bachelor's thesis). McGill University, Montréal, Québec, Canada. -->

<!-- **Thériault, R.**, Baron, A., & Cowell, B.(2012). *Comment les activités artistiques peuvent développer l'estime de soi chez les jeunes marginalisés : une intervention en cirque social à la maison des jeunes Kekpart* (Collegial thesis). Cégep Édouard-Montpetit, Longueuil, Québec, Canada. -->