---
output: html_document
---

\setlength{\parindent}{0in}
\setlength{\leftskip}{0in}
\normalsize

# Varia

## Professional Affiliations

\scriptsize

```{r Affiliations}
data <- rbind(
  
  tibble(
    when = "2022/02 – Present",
    with = "Canadian Psychological Association"),
  
  tibble(
    when = "2021/01  – Present",
    with = "Institut des sciences cognitives (UQAM)"),
  
  tibble(
    when = "2016/09 – Present",
    with = "International Positive Psychology Association"),
  
  tibble(
    when = "2016/02 – Present",
    with = "Psychologists for Social Responsibility"),
  
  tibble(
    when = "2015/09 – Present",
    with = "Canadian Positive Psychology Association")
)

detailed_entries(data, with, when, .protect = FALSE)
```

## Conferences Attended

```{r Conferences}
data <- rbind(
  
  tibble(
    Name = "6th World Congress on Positive Psychology",
    where = "Melbourne, Australia",
    Date = "2019/07"),
  
  tibble(
    Name = "Mind \\& Life Summer Research Institute",
    where = "Garrison, New York",
    Date = "2019/06"),
  
  tibble(
    Name = "Congress of the Humanities and Social Sciences",
    where = "Vancouver, BC",
    Date = "2019/06"),
  
  tibble(
    Name = "XXI World Congress of Medical and Clinical Hypnosis",
    where = "Montréal, QC",
    Date = "2018/08"),
  
  tibble(
    Name = "Mind \\& Life Summer Research Institute",
    where = "Garrison, New York",
    Date = "2018/06"),
  
  tibble(
    Name = "4th Canadian Conference on Positive Psychology",
    where = "Toronto, ON",
    Date = "2018/05"),
  
  tibble(
    Name = "5th World Congress on Positive Psychology",
    where = "Montréal, QC",
    Date = "2017/06"),
  
  tibble(
    Name = "Psychologie Positive au sein de la francophonie, perspectives et prospective",
    where = "Montréal, QC",
    Date = "2017/06"),
  
  tibble(
    Name = "Research Day of the Douglas Hospital Research Centre",
    where = "Montréal, QC",
    Date = "2017/05"),
  
  tibble(
    Name = "8th Annual LDI Scientific",
    where = "Montréal, QC",
    Date = "2017/05"),
  
  tibble(
    Name = "3rd Canadian Conference on Positive Psychology",
    where = "Niagara-on-the-Lake, ON",
    Date = "2016/05"),
  
  tibble(
    Name = "Psychology Undergraduate Research Day",
    where = "McGill University",
    Date = "2015/04"),
  
  tibble(
    Name = "6th Annual Faculty of Arts Undergraduate Research Event",
    where = "McGill University",
    Date = "2015/01")
  
)

data <- data %>% 
  mutate(Name = paste0("\\hspace{0.5cm} ", Name))

brief_entries(data, Name, Date, where, .protect = FALSE)
```

## Research Interests

Positive & moral psychology, contemplative practices, Theory of Mind, empathy, self-regulatory strength, Self-Determination Theory, bodily self-consciousness, multisensory integration, anomalous experiences

## Technical Skills

Including: R, Rstudio, Shiny, GitHub, Inquisit, Wowchemy, Netlify, SPSS, MATLAB, ActiView, Brainstorm, Brain Analyzer, Qualtrics, Survey Monkey, LimeSurvey, Microsoft Office suite, Adobe Software, WordPress.

## Languages

French (native) and English (fluent)

## Activities And Interests

Martial arts (Jeet Kune Do & others), breakdance, parkour/free running, skateboard, gymnastics, yoga, salsa)